Learning by Teaching a Robot: the Case of Handwriting

### 2015-07-08 main.tex
Detailled examples of 'g'

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{cowriter-g}
    \caption{\small \label{fig:sampleLetters} \textbf{Generating bad letters}:
        effect of varying the first five eigenvalues (rows) of the shape model
        of ``g'' by different factors (columns). The percentage of the total
        variance in the dataset explained by each eigenvalue is shown      on
        the appropriate row.}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{cowriter-g}
    \caption{\small \label{fig:sampleLetters} \textbf{Generating bad letters}:
        effect of varying the first five eigenvalues (rows) of the shape model
        of ``g'' by different factors (columns). The percentage of the total
        variance in the dataset explained by each eigenvalue is shown      on
        the appropriate row. Examples noted A, B, C, D illustrate how the
        PCA-based approach allows to \emph{automatically} generate letters whose
        errors can be \emph{semantically} interpreted: A has a too large bottom
        loop, B has a wide top loop, the bottom loop of C is not correctly
        closed, the top loop of D is not closed.}
